On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-02-15 paper/cav_determinisim_main.tex

This research has in part been funded by the ROBOPILOT and CAPRI projects. Both projects are part-funded by the Centre for Connected and Autonomous Vehicles (CCAV), delivered in partnership with Innovate UK under grant numbers 103703 (CAPRI) and 103288 (ROBOPILOT), respectively.
The Associate Editor for this paper was ....(\textit{Corresponding author: Abanoub Ghobrial.})

A.Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
G.Chance (e-mail: greg.chance@bristol.ac.uk), 
K.McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
K.Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road,  Bristol, BS8 1UQ, United Kingdom.

S.Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
T.Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England,Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.

>>>>

\textit{Abanoub Ghobrial and Greg Chance contributed equally to this paper and are both corresponding authors.}
%

This research has in part been funded by the ROBOPILOT and CAPRI projects. Both projects are part-funded by the Centre for Connected and Autonomous Vehicles (CCAV), delivered in partnership with Innovate UK under grant numbers 103703 (CAPRI) and 103288 (ROBOPILOT), respectively.
% The Associate Editor for this paper was ....

Abanoub Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
Greg Chance (e-mail: greg.chance@bristol.ac.uk), 
Kevin McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
Kerstin Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road,  Bristol, BS8 1UQ, United Kingdom.

Severin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England,Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.
